\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb,amsfonts,graphicx}
\usepackage{hyperref}

\newcommand{\Pp}{\emph{\emph{P}}}

\begin{document}

\title{Final Statistics Presentation}
\author{Mr. Grant}
\maketitle

\textbf{Due Date:} Wednesday or Thursday (depending on your group) August 2nd or 3rd \\

You must give a final presentation on the survey/study you conducted last Friday. Each group's presentation should be around 8 minutes (a minute or two over or under is okay). That means each person in the group should talk for about 2 minutes.

The point of this presentation is to describe your study and the conclusions you've drawn from the data you gathered \textit{to your peers} (your peers in this class are your audience, so you can and should use statistical terminology).

Your presentation should be structured as follows:
\begin{enumerate}
	\item Title Slide: who did the research? Title of the study?
	\item Introduce the Problem: what is the research question, and why is it interesting?
	\item Research Methods (2-3 slides): how did you perform the survey? What were the survey questions? Be detailed, but don't just fill up space.
	\item Data (1 slide): summarize the data you gathered in a simple, understandable way (perhaps a table).
	\item Results (1-2 slides): present the results of the study. A graph or table that clearly answers the research question is a must.
	\item Biases: what sampling biases might have distorted your study (and how do you suspect they distorted it). Could you have done anything better?
	\item Conclusion: in words, what have you learned?
\end{enumerate}

\end{document}
